Large scale risks from pesticides in small streams

### 2016-11-14 article.tex
final fixes before submission

The first quarter showed the lowest RQ and probability of exceeding LOQ.
Both increased during summer months and decreased towards the end of the year.
There was a 2.5-folder higher probability of exceeding LOQ in $Q2$ (10.6\%) than in $Q1$ (4.6\%).
The differences were less pronounced for the mean value of RQ and with less precision (Figure~\ref{fig:fig5}, bottom). 
Individual compounds showed different temporal patterns (see Supplemental Table~S4).

\begin{figure}[ht]
  \includegraphics[width=0.8\textwidth]{figure5.pdf}
  \caption{Summarised coefficients (and their 95\% CI) for precipitation (top row) and quarter (bottom row) from a meta-analysis of the 24 modelled compounds. Left column: coefficients for mean RQ ($\mu$), right column: coefficients for probability to exceed LOQ ($\nu$). 
  Coefficients are shown on the link scale (see Eq.~\ref{eqn:eqn4}).
  Single compound coefficients are provided in Supplemental Table~S4 and Figure~S7).
  }
  \label{fig:fig5}
\end{figure}

@@

\subsection{Effect of precipitation on pesticide risk}
Our results revealed that pesticide sampling for chemical monitoring in Germany is mainly performed when no precipitation occurs. 
Nevertheless, we found a 36\% higher RQ if samples were taken after rainfall events. 
Samples taken on the day of a rainfall event showed less risk than samples taken one day after a rainfall event.
This could be explained by the sampling preceding the rainfall event and the delay between the start of a rain event and the peak in discharge or runoff. 
The effects of precipitation were more pronounced for the probability to exceed LOQ, with smaller effect sizes for the absolute value of RQ. 
This could be attributed to a higher variability of absolute concentrations.
Overall, our results indicate that current pesticide monitoring relying on grab sampling, largely disconnected from precipitation events, underestimates pesticide risks.
Automatic event-driven samplers \citep{stehle_probabilistic_2013} and passive samplers \citep{fernandez_calibration_2014,moschet_evaluation_2015} may help overcome these shortcomings and provide a better representation of risks, especially for small water bodies \citep{lorenz_specifics_2016}.

@@

\subsection{Pesticides in small streams}
Our results suggest that small streams are frequently exposed to ecologically relevant pesticide concentrations.
In one-quarter of small streams RACs were exceeded at least once.
\citet{stehle_pesticide_2015} found the highest percentage of RAC exceedances for organophosphate insecticides. 
By contrast, we found that that neonicotinoid insecticides have highest exceedances of RACs, followed by the organophosphate chlorpyrifos. 
This difference can be attributed to the low sample size for neonicotinoid insecticides in their study (n = 33) compared to the dataset presented here (for example 3,540 samples of Thiacloprid, Figure~\ref{fig:fig6}). 
Overall, our results suggest that neonicotinoids may currently pose a high risk to freshwater ecosystems. 
Moreover, our results add further evidence to the growing literature on the risks arising from neonicotinoids for aquatic \citep{morrissey2015neonicotinoid} and terrestrial \citep{pisa2015effects} ecosystems.

Compared to \citet{stehle_pesticide_2015} we found higher rates of RAC exceedances for insecticides.
They found exceedances in 37.1\% of insecticide measurements \textgreater LOQ (n = 1352, 23 insecticides), whereas, we found exceedances in 67\% of insecticide measurements with RACs \textgreater LOQ (n = 1855, 22 insecticides). 
This could be attributed to different insecticides considered and different underlying RACs.
Our study has only 7 insecticides with RACs in common with the insecticides investigated by \citet{stehle_pesticide_2015}.
Moreover, all RACs were lower in our study (average = -0.71 $\mu g/L$, range = [-2.757; -0.005]). 
Nevertheless, it must be noted that the dataset compiled here comprised only samples from grab sampling, which may considerably underestimate pesticide exposure \citep{stehle_probabilistic_2013, Xing_Chow_Rees_Meng_Li_Ernst_Benoy_Zha_Hewitt_2013}.

>>>>

The first quarter showed the lowest RQ and probability of exceeding LOQ.
Both increased during summer months and decreased towards the end of the year.
There was a 2.5-fold higher probability of exceeding LOQ in $Q2$ (10.6\%) than in $Q1$ (4.6\%).
The differences were less pronounced for the mean value of RQ and with less precision (Figure~\ref{fig:fig5}, bottom). 
Individual compounds showed different temporal patterns (see Supplemental Table~S4).

\begin{figure}[ht]
  \includegraphics[width=0.8\textwidth]{figure5.pdf}
  \caption{Summarised coefficients (and their 95\% CI) for precipitation (top row) and quarter (bottom row) from a meta-analysis of the 22 modelled compounds. Left: coefficients for mean RQ ($\mu$), right: coefficients for probability of exceeding LOQ ($\nu$). 
  Coefficients are shown on the link scale (see Eq.~\ref{eqn:eqn4}).
  Single compound coefficients are provided in Supplemental Table~S4 and Figure~S7).
  }
  \label{fig:fig5}
\end{figure}

@@

\subsection{Effect of precipitation on pesticide risk}
Our results revealed that pesticide sampling for chemical monitoring in Germany is mainly performed when no precipitation occurs. 
Nevertheless, we found a 36\% higher RQ if samples were taken after rainfall events. 
Samples taken on the day of a rainfall event showed less risk than samples taken one day after a rainfall event.
This could be explained by the sampling preceding the rainfall event and the delay between the start of a rain event and the peak in discharge or runoff. 
The effects of precipitation were more pronounced for the probability to exceed LOQ, with smaller effect sizes for the absolute value of RQ. 
This may be explained by a higher variability of absolute concentrations.
Overall, our results indicate that current pesticide monitoring relying on grab sampling, largely disconnected from precipitation events, underestimates pesticide risks.
Automatic event-driven samplers \citep{stehle_probabilistic_2013} and passive samplers \citep{fernandez_calibration_2014,moschet_evaluation_2015} may help overcome these shortcomings and provide a better representation of risks, especially for small water bodies \citep{lorenz_specifics_2016}.

@@

\subsection{Pesticides in small streams}
Our results suggest that small streams are frequently exposed to ecologically relevant pesticide concentrations.
In one-quarter of small streams RACs were exceeded at least once.
\citet{stehle_pesticide_2015} found the highest percentage of RAC exceedances for organophosphate insecticides. 
By contrast, we found that neonicotinoid insecticides have highest exceedances of RACs, followed by the organophosphate chlorpyrifos. 
This difference can be attributed to the low sample size for neonicotinoid insecticides in their study (n = 33) compared to the dataset presented here (for example 3,540 samples of Thiacloprid, Figure~\ref{fig:fig6}). 
Overall, our results suggest that neonicotinoids may currently pose a high risk to freshwater ecosystems. 
Moreover, our results add further evidence to the growing literature on the risks arising from neonicotinoids for aquatic \citep{morrissey2015neonicotinoid} and terrestrial \citep{pisa2015effects} ecosystems.

Compared to \citet{stehle_pesticide_2015} we found higher rates of RAC exceedances for insecticides.
They found exceedances in 37.1\% of insecticide measurements \textgreater LOQ (n = 1352, 23 insecticides), whereas, we found exceedances in 67\% of insecticide measurements with RACs \textgreater LOQ (n = 1855, 22 insecticides). 
This could be attributed to different insecticides considered and different underlying RACs.
Our study has only 7 insecticides with RACs in common with the insecticides investigated by \citet{stehle_pesticide_2015}.
Moreover, all RACs were lower in our study (average difference = -0.71 $\mu g/L$, range = [-2.757; -0.005]). 
Nevertheless, it must be noted that the dataset compiled here comprised only samples from grab sampling, which may considerably underestimate pesticide exposure \citep{stehle_probabilistic_2013, Xing_Chow_Rees_Meng_Li_Ernst_Benoy_Zha_Hewitt_2013}.
